A Nonlinear Model for Dispersion-Tuned Actively Mode-Locked Lasers

### 2018-12-23 Thesis/Model/Model.tex
Told TeXWorks what the main file was

@@

\begin{table}
\begin{center}
\begin{tabular}{|l|l|}
\hline
Parameter & Value \\
\hline
$\Es$ & $10^3$--$10^4 \text{ pJ}$ \\
$\gamma$ & $0.001$--$0.01 \text{ W}^{-1} \text{m}^{-1}$ \cite{agrawal2013} \\
$g_0$ & $1$--$10 \text{ m}^{-1}$ \\
$\beta_2^g L_D$ & $10$--$2000 \text{ ps}^2$ \cite{burgoyne2014, agrawal2013, litchinitser} \\
$\beta_2^f$ & $-50$--$50 \text{ ps}^2/ \text{km}$ \cite{burgoyne2014, agrawal2013} \\
$T_M$ & $15$--$150 \text{ ps}$ \cite{burgoyne2014} \\
$L$ & $10$--$100 \text{ m}$ \\
$L_g$ & $1$--$4 \text{ m}$ \cite{burgoyne2014, shtyrina, yarutkina} \\
$L_f$ & $0.15$--$1 \text{ m}$ \\
\hline
\end{tabular}
\caption{Orders of magnitude of various parameters.}
\label{tab:values}
\end{center}
\end{table}

>>>>

% !TeX root = ../Thesis.tex

@@

\begin{table}
\begin{center}
\begin{tabular}{lclc}
Parameter & Symbol & Value & Source \\
\noalign{\global\arrayrulewidth=1.5pt}\hline
Saturation Energy & $\Es$ & $10^3$--$10^4 \text{ pJ}$ & \cite{burgoyneemail} \\
Fibre Nonlinearity & $\gamma$ & $0.001$--$0.01 \text{ W}^{-1} \text{m}^{-1}$ & \cite{agrawal2013} \\
Small Signal Gain & $g_0$ & $1$--$10 \text{ m}^{-1}$ & \cite{burgoyneemail} \\
Grating Dispersion & $\beta_2^g L_D$ & $10$--$2000 \text{ ps}^2$ & \cite{burgoyne2014, agrawal2013, litchinitser} \\
Fibre Dispersion & $\beta_2^f$ & $-50$--$50 \text{ ps}^2/ \text{km}$ & \cite{burgoyne2014, agrawal2013} \\
Modulation Time & $T_M$ & $15$--$150 \text{ ps}$ & \cite{burgoyne2014, burgoyneemail} \\
Length of Cavity & $L$ & $10$--$100 \text{ m}$ & \cite{burgoyneemail} \\
Length of Gain Fibre & $L_g$ & $1$--$4 \text{ m}$ & \cite{burgoyne2014, shtyrina, yarutkina} \\
Length of Fibre & $L_f$ & $0.15$--$1 \text{ m}$ & \cite{burgoyneemail} \\
\hline
\end{tabular}
\caption{Orders of magnitude of various parameters.}
\label{tab:values}
\end{center}
\end{table}
